Peaks Over Threshold for Bursty Time Series

### 2018-05-10 article_springer/index.Rmd
fix \eqref
add toc
link to pdf

  This article generalizes the Peaks Over Threshold (POT) model to the setting 
  where inter-event times are heavy-tailed. For high thresholds and 
  infinite-mean waiting times, we show that the times between threshold 
  crossings are Mittag-Leffler distributed, and thus form a "fractional 
  Poisson Process" which generalizes the standard Poisson Process.
  We provide graphical means of estimating model parameters and assessing 
  model fit. Along the way, we apply our inference method to a real-world
  bursty time series, and 
  show how the memory of the Mittag-Leffler distribution affects 
  the predictive distribution for the time until the next extreme event. 
bibliography: CTRMstats.bib
output: 
  bookdown::html_document2: 
    theme: journal
params:
  tail: 0.8
  n: 10000
preamble: |
  \usepackage{amssymb}
---

@@

>>>>

  This article generalizes the Peaks Over Threshold (POT) model to the setting 
  where inter-event times are heavy-tailed. For high thresholds and 
  infinite-mean waiting times, we show that the times between threshold 
  crossings are Mittag-Leffler distributed, and thus form a "fractional 
  Poisson Process" which generalizes the standard Poisson Process.
  We provide graphical means of estimating model parameters and assessing 
  model fit. Along the way, we apply our inference method to a real-world
  bursty time series, and 
  show how the memory of the Mittag-Leffler distribution affects 
  the predictive distribution for the time until the next extreme event. 
bibliography: CTRMstats.bib
site: bookdown::bookdown_site
output: 
  bookdown::html_document2: 
    toc: true
    toc_float: true
    theme: readable
params:
  tail: 0.8
  n: 10000
preamble: |
  \usepackage{amssymb}
---

@@

(You can download a [pdf version of this paper](https://arxiv.org/pdf/1802.05218).)
